Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-14 paper.tex
Discuss meancontquiv figs

% In this section, show mean velocity contours/quivers

>>>>

In order to visualize the mean velocity field, vector arrows for the mean
cross-stream and vertical components are superimosed on top of contours of the
streamwise component at $X/D=1$ in Figure~\ref{fig:mean-velocity}. Both CFD
models predict the general structure of the mean velocity well, though the SA
case has slightly larger vertical mean flows, which could be due to stronger tip
vortex generation, or lower diffusivity compared with the SST model. Additional
discrepancies between CFD and experiments may be due to the top slip boundary
condition versus the experiment's free surface.
